---
title: "Homework 2"
author: "Diana Perez"
date: "11/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Start of homework

```{r,eval = FALSE}
##this code will NOT be run but will be shown

##Basic calculations
1+1  #Add
2-4  #Substract
12/3  #Divide
2*4   #Multiply
3^2   #Power
3*(1+2) #Pharentesis

## R uses standard mathematical order of opertions/precendence (1.Exponents, 2. Multiplication and Division, 3. Addition and Substraction)

```


```{r,eval = FALSE}}
##This code will be run and shown in the Rmarkdown
##Assigning values to objects
a <- 1
d <- 10
h <-  (1+3)^2 - (1/3)(2)

##Vectors
a <- c(1,2,3,4,5) #Numeric Vector

b <- c(6,7,8,9,10) #Numeric Vector

length(a) ##Length of the vector of number

c(a,b) #combine vectors into a new vector

q <- c(10,8,9,7,b,3) #Make a new vector that includes other vector

q[2] #Second value of the vector

b[c(3,5)] #return value third and fifth of the vector

f <- a * 4 #Multiply a vector

my vec <- c(1,3,2)
names(my_vec) <- c("a", "b", "c") ##assign names to the vector using the names() function

sorted_vec <- sort(my_vec) #Sort the values in the vector

sorted_vec <- sort(my_vec, decreasing = TRUE) #Sort the values of the vector by decreasing

##runif fuction runif(n,min,max) ; it generates uniformly distributed random numbers

x <- runif(10, 0, 20)
x < 5 #Logical argument

x[x>13] #return only the numbers from the vector which are greater than 13

mean(x) ##Mean function

round(c(1.243,2.567,3.657)) #round the values in the vector

```

##Programing 
```{R ,eval = FALSE}
##this code will NOT be run but will be shown}

#For loop
for(variable in sequence){
  #Do something
}
##For examples

for(i in 1:10){
  x1 <- i^2
  print(x1)
}

x2 <- c("Max", "Tina", "Lindsey", "Anton")

for(i in x2) {
  print(paste("The name," i, "consists of", nchar(i), "characters.")
}

##IF 

if(condition) {
  #Do something
} else {
  #Do something different
}

for(i in 1:10) {
  x5 <- i^2
  print(x5)
  
  if(i>=5){
    break
  }
}

if(i>3){
  print("yes")
} else {
  print("No")
}

##Creating a new function
function_name <- function(var){
  #Do something
  return(new_variable)
}

##Example of a function
square <- function(x){
  squared <- x*x
  return(squared)
}

#Matrix function
m <- matrix(x, nrow, ncol)

#List
l <- list(x=1:5)

#Reading data
df <-read.table("file.txt")
df <- read.csv("file.csv")
